### 2015-04-28 evaluation.tex
various updates in evaluation

\noindent
\textbf{Benchmarks}\xspace\xspace We evaluate our methodology against \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel. To thoroughly test \whoop against the Linux driver APIs, we chose drivers from many different domains: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. Further, we focused on choosing non-trivial drivers (e.g. large number of entry points, deep nesting of entry point helper functions, complex use of locking, use of function pointers, etc). We manually modeled the environment for all these drivers, a process that required more than a month of work.

@@

We can see that, in general, \whoop reports (many) more races than \corral. This is expected because \whoop over-approximates the original driver for soundness: if a race exists, the tool will report it (assuming tool and model correctness), but \whoop can, and does, report false races. On the contrary, \corral reports only real races, but does that under pre-defined bounds and thus can miss races.

>>>>

\noindent
\textbf{Benchmarks}\xspace\xspace We evaluate our methodology against \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel. We chose drivers from many different domains: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. Further, we focused on choosing non-trivial drivers (e.g. large number of entry points, deep nesting of entry point helper functions, complex use of locking, use of function pointers, etc). We manually modeled the environment for all these drivers, a process that required more than a month of work.

@@

We can see that, in general, \whoop reports more races than \corral. This is expected because \whoop over-approximates the original driver for soundness: if a race exists, the tool will report it (assuming tool and model correctness), but \whoop can, and does, report false races. On the contrary, \corral is precise, but can miss races as it explores the driver under pre-defined bounds. Further, a common problem for \corral is loop coverage. To tackle this we enable the build-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice.
